%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{report}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PDF output?
\newif\ifpdf
\ifx\pdfoutput\undefined
  \pdffalse
\else
  \pdfoutput=1
  \pdftrue
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{subfigure}
\setlength{\parindent}{0pt}
\ifpdf
  \RequirePackage[pdftex, colorlinks=true, pdfstartview=FitH, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
  \pdfinfo{
  /Title    (Verdict Library Reference Manual)
  /Author   (C. J. Stimpson, C. D. Ernst, P. Knupp, P. P. Pebay, and D. Thompson)
  /Keywords ()
  }
\else
  \RequirePackage{hyperref}
\fi
\input{VerdictMathMacros}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{.}{./png/}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Sf}{\mathfrak{S}_4}
\newcommand{\verd}{\textsf{Verdict}}
\newcommand{\cubit}{\textsf{CUBIT}}
\newcommand{\verde}{\textsf{VERDE}}
\newcommand{\vtk}{\textsf{VTK}}
\newcommand{\PV}{\textsf{ParaView}}
\newcommand{\nsup}{\textrm{Not supported}}
\newcommand{\dgr}{\ensuremath{^{\circ}}}
\newcommand{\normvec}[1]{\big\lVert{\vec#1}\big\rVert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The \verd{} Library Reference Manual}
\author{C. J. Stimpson\\
        Elemental Technologies, Inc.\\
        17 N. Merchant St.\\
        American Fork, UT 84003, U.S.A.\\
        \texttt{clinton@elemtech.com}
        \and
        C. D. Ernst\\
        Elemental Technologies, Inc.\\
        17 N. Merchant St.\\
        American Fork, UT 84003, U.S.A.\\
        \texttt{corey@elemtech.com}
        \and
        P. Knupp\\
        Sandia National Laboratories\\
        M.S. 1318, P.O. Box 5800\\
        Albuquerque, NM 87185, U.S.A.\\
        \texttt{pknupp@sandia.gov}
        \and
        P. P. P\'ebay\\
        Sandia National Laboratories\\
        M.S. 9051, P.O. Box 969\\
        Livermore, CA 94550, U.S.A.\\
        \texttt{pppebay@sandia.gov}
        \and
        D. Thompson\\
        Sandia National Laboratories\\
        M.S. 9152, P.O. Box 969\\
        Livermore, CA 94550, U.S.A.\\
        \texttt{dcthomp@sandia.gov}
}
\date{April 2007}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\verd\ is a collection of subroutines for evaluating the geometric qualities
of triangles, quadrilaterals, tetrahedra, and hexahedra using a variety of
metrics.
A metric is a real number assigned to one of these shapes depending on its
particular vertex coordinates.
These metrics are used to evaluate the input to finite element, finite volume,
boundary element, and other types of solvers that approximate the solution to
partial differential equations defined over regions of space.
The geometric qualities of these regions is usually strongly tied to the
accuracy these solvers are able to obtain in their approximations.

The subroutines are written in C++ and have a simple C interface.
Each metric may be evaluated individually or in combination.
When multiple metrics are evaluated at once, they share common
calculations to lower the cost of the evaluation.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section*{Acknowledgements}
The authors would like to acknowledge, in no particular order, the
following individuals:
Jason Shepherd, Robert Kerr, Rob Leland, Tim Tautges, Ray Meyers, Karl
Merkley, Greg Sjaardema, David White, and Scott Mitchell.\\

Authors affiliated with Sandia National Laboratories were supported by
the United States Department of Energy, Office of Defense
Programs. Sandia is a multiprogram laboratory operated by Sandia
Corporation, a Lockheed-Martin Company, for the United States
Department of Energy under contract DE-AC04-94-AL85000.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\tableofcontents
\listoffigures
%\listoftables
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{00-Introduction}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{10-Instructions}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{API}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Tri}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Quad}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Tet}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Hex}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{OtherEl}
\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{*}
\bibliographystyle{plain}
\bibliography{Verdict-Manual-2007}
\addcontentsline{toc}{section}{References}
%\printindex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
